Online Supplement: Demographic costs of sexually antagonistic polymorphism in outcrossers and simultaneous hermaphrodites \\ \textit{The~American~Naturalist}

### 2021-03-26 doc/Supplements/SupplementaryMaterial.tex
Draft ready for friendly review
Made minor edits, new title, added Supplementary material .tex file.

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]
\usepackage{fancyhdr}
\pagestyle{fancy}

%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%
%
% Customize the line below with the last name of your first author and
% the short title of your MS. You can comment authorship information out
% while your MS is undergoing double-blind review.
%
\rhead{Supplement to AUTHOR-NAME et al., ``SHORT TITLE,'' \textit{Am.~Nat.}}
\setlength{\headsep}{0.3in}  
\lhead{}

@@

\title{Online Supplement: \\ 
\LaTeX{} Template for Author-Supplied Supplementary PDFs, \\ 
\textit{The~American~Naturalist} }

@@

%%%%%%%%%%%%%%%%%%%%%
% Authorship
%%%%%%%%%%%%%%%%%%%%%
% Please remove authorship information while your paper is under review,
% unless you wish to waive your anonymity under double-blind review. You
% will need to add this information back in to your final files after
% acceptance.
%
% Once accepted for publication, author-supplied PDFs should have a 
% title page that includes (at least) the authors' names, the title of 
% the MS, and the name of the journal. It should also have a header and
% page numbers.

\author{Owen E. Cook$^{1,\ast}$ \\ 
Generic H. Collaborator$^{2,\dag}$ \\ 
Additional Q. Expert$^{3}$}

\date{}

@@

\noindent{} 1. University of Chicago, Chicago, Illinois 60637;

\noindent{} 2. University of Toronto, Toronto, Ontario M5S 1A5, Canada;

\noindent{} 3. Middle Eastern Technical University, Çankaya, Ankara 06800, Turkey.

\noindent{} $\ast$ Corresponding author; e-mail: amnat@uchicago.edu.

\noindent{} $\dag$ Deceased.

>>>>

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\setlength{\headheight}{13.6pt}
%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%
%
% Customize the line below with the last name of your first author and
% the short title of your MS. You can comment authorship information out
% while your MS is undergoing double-blind review.
%
\rhead{Supplement to Olito \& de Vries., "Costs of SA polymorphism" \textit{Am.~Nat.}}
\setlength{\headsep}{0.3in}  
\lhead{}

@@

\title{Online Supplement: Demographic costs of sexually antagonistic polymorphism in outcrossers and simultaneous hermaphrodites \\ 
%\LaTeX{} Template for Author-Supplied Supplementary PDFs, \\ 
\textit{The~American~Naturalist} }

@@

%%%%%%%%%%%%%%%%%%%%%
% Authorship
%%%%%%%%%%%%%%%%%%%%%
% Please remove authorship information while your paper is under review,
% unless you wish to waive your anonymity under double-blind review. You
% will need to add this information back in to your final files after
% acceptance.
%
% Once accepted for publication, author-supplied PDFs should have a 
% title page that includes (at least) the authors' names, the title of 
% the MS, and the name of the journal. It should also have a header and
% page numbers.
\author{Colin Olito$^{1,\ast}$ \\ 
Charlotte de Vries$^{2}$}

\date{\today}

@@

\noindent{} 1. Department of Biology, Lund University, Lund 223 62, Sweden;

\noindent{} 2.  Department of Evolutionary Biology and Environmental Studies, University of Zurich, Zurich CH-8057, Switzerland;

\noindent{} $\ast$ Corresponding author; e-mail: \url{colin.olito@gmail.com}
